Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Comments

\maciek{TODO: discuss the title. We should not claim tight bounds with an exponential gap. Reviewers will point this out, as this is an easy thing to criticize in the review.}

@@

\maciek{The text before the proof should have two parts: a description of adversary components and then general intro to the proof.}

@@

\maciek{Here: we abstract from the value of $\alpha$, but works for any alpha.}

@@

  \maciek{This paragraph should be before the proof, merged with section about adversary components.}
  We join some nodes into components, and produce the input sequence by observing actions of \ALG{} with respect to nodes of these components.
	If \ALG{} at any point splits a component
	(i.e., spreads its nodes over two or more clusters),
	then we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
	If \ALG{} never collocates them, then it is not competitive.

@@

\maciek{Start with referencing the table of results, saying that some results are known already. And really emphasize here that we now have an improved lower bound from the previous section, as that model was a subproblem.}

@@

Corollary: Algorithm DET2 is $O(\ell \cdot k\cdot k^k)$-competitive.

@@

       \item lower and upper bound $k+1$ for two clusters, perfect partition and the optimal configuration reachable within one swap

>>>>

@@

\maciek{The text before the proof should have two parts: a description of ground sets and then general intro to the proof.}

@@

\maciek{Note that the lower bound works for any value of $\alpha$, and we just use the number of migrations}

@@

  \maciek{This paragraph should be before the proof, merged with section about ground sets (i.e., adversary components.)}
  We join some nodes into components, and produce the input sequence by observing actions of \ALG{} with respect to nodes of these components.
	If \ALG{} at any point splits a component
	(i.e., spreads its nodes over two or more clusters),
	then we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
	If \ALG{} never collocates them, then it is not competitive.

@@

\maciek{Start with referencing the table of results, saying that some results are known already in the literature. And emphasize here that we now have an improved lower bound from the previous section, as that model was a subproblem.}

@@

Corollary: Algorithm DET2 is $O(\ell \cdot k \cdot \min \{ \ell, k^k \})$-competitive.

@@

       \item lower and upper bound $k+1$ for two clusters, perfect partition and the optimal configuration reachable within one swap
       \item 
       The bound $(k \cdot \ell - k - \ell) / 2$ can be easily improved to $(k \cdot \ell - k - 1) / 2$ by playing a simple caching game in the first cluster, instead of just giving away the $k-1$ "blocker" (the caching game would build it gradually)
